\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{orcidlink}
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}
\usepackage{calc}

% Settings
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

% Commands
\newcommand{\spacedentry}[2]{%
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    #1 & #2 \\
  \end{tabular*}
}
\newcommand{\datedentry}[2]{%
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.75\textwidth} r}
    #1 & #2 \\
  \end{tabular*}
}
\newcommand{\sectionheader}[1]{%
{\Large{#1}}
\vspace{2ex}
\hrule
\vspace{2ex}
}
\newlength{\titlewidth}

\newcommand{\narrowpar}[2]{%
  \settowidth{\titlewidth}{#1}%
  \begin{minipage}{0.80\textwidth}%
    \hangindent=\titlewidth
    \hangafter=1
    #1%
    \if\relax\detokenize{#1}\relax
      % do nothing
    \else
      ~%
    \fi
    #2%
  \end{minipage}%
}


% Document

\begin{document}
{\LARGE{\textbf{Nathaniel Dene Hoffman}}}\\
\vspace{-2ex}
\hrule
\vspace{2ex}

% Contact

\spacedentry{Carnegie Mellon University}{\href{mailto:dene@cmu.edu}{dene@cmu.edu}}
\spacedentry{Department of Physics}{Phone: +1\,(636)\,432-4128}
\spacedentry{5000 Forbes Avenue}{\href{https://www.denehoffman.com}{www.denehoffman.com}}
\spacedentry{Pittsburgh, PA 15213}{\orcidlinkc{0000-0002-8865-2286}}

\vspace{1em}
% Education
\sectionheader{Education}

\textbf{Carnegie Mellon University}\\
Ph.D., Physics, 2019\textendash Present.\\
Field: Nuclear and Particle Physics\\
M.S., Physics, 2021.
\\\\
\textbf{Case Western Reserve University}\\
B.S., Physics, 2019.\\
B.A., Music, 2019.\\

% Research
\sectionheader{Research}

\datedentry{\textbf{Department of Physics, CMU} }{2019\textendash Present}
Ph.D. Candidate (Advisor: Reinhard Schumacher)\\
\narrowpar{Thesis:}{\textit{Photoproduction of $K_S^0$ Pairs at GlueX} (in progress)}\\

\datedentry{\textbf{Department of Physics, CMU}}{2020}\\
Research Assistant (Advisor: Michael Widom)\\
\narrowpar{Project:}{\textit{Cluster Variation Method Analysis of BCC Heusler Alloys}}\\

\datedentry{\textbf{Department of Physics, CWRU}}{2016\textendash 2019}
Research Assistant (Advisor: Giuseppe Strangi)\\
\narrowpar{Project:}{\textit{Material Properties and Fabrication of Thin-Film Metamaterials}}\\

% Teaching
\sectionheader{Teaching}

\datedentry{\textbf{Department of Physics, CMU}}{2019\textendash 2020}
Teaching Assistant, Basic Experimental Physics\\

\datedentry{\textbf{Department of Physics, CWRU}}{2017\textendash 2019}
Teaching Assistant, Honors Introduction to Electromagnetism\\

% Awards
\sectionheader{Awards and Fellowships}
\datedentry{\textbf{Michelson-Moreley Scholarship}
CWRU}{2015\textendash 2019}

\newpage

% Talks
\sectionheader{Talks}

\datedentry{\textbf{Jefferson Lab Users Organization Annual Meeting} (upcoming)}{June 25, 2025}
\narrowpar{Title:}{\textit{Spectroscopy with K-short Mesons from GlueX} (invited)}\\

\datedentry{\textbf{PWA13/ATHOS8}}{May 28, 2024}
\narrowpar{Title:}{\textit{Photoproduction of $K_S$ Pairs at GlueX}}\\

\datedentry{\textbf{APS April Meeting}}{April 17, 2023}
\narrowpar{Title:}{\textit{Photoproduction of Mesons Decaying into $K_SK_S$ at GlueX}}\\

\datedentry{\textbf{Jefferson Lab Users Organization Meeting at APS}}{April 16, 2023}
\narrowpar{Title:}{\textit{GlueX/Hall D Overview} (invited)}\\

\datedentry{\textbf{APS Division of Nuclear Physics}}{October 14, 2021}
\narrowpar{Title:}{\textit{Meson and Baryon Photoproduction using $\gamma p \to K_SK_Sp$ at GlueX}}\\

% Projects
\sectionheader{Projects}

\textbf{laddu} is a library for analysis of particle physics data. It is intended to be a simple and efficient alternative to some of the other tools out there. \texttt{laddu} is written in Rust with bindings to Python via PyO3 and maturin. The goal of this project is to allow users to perform complex amplitude analyses (like partial-wave analyses) without complex code or configuration files. It additionally supports the Message Passing Interface (MPI) protocol for parallelization in high-perfomance computing environments. \texttt{laddu} prioritizes the Parquet data format while providing methods to read and convert ROOT files.\\
\textbf{Link:} \href{https://github.com/denehoffman/laddu}{https://github.com/denehoffman/laddu}\\

\textbf{ganesh} is a Rust crate providing common optimization algorithms as well a straightforward, trait-based interface to create extension algorithms. It provides pure-Rust implementations of the L-BFGS-B and Nelder-Mead minimization algorithms along with implementations of the Affine-Invariant Ensemble Sampler and Ensemble Slice Sampler for Markov chain Monte Carlo analyses.\\
\textbf{Link:} \href{https://github.com/denehoffman/ganesh}{https://github.com/denehoffman/ganesh}\\

\textbf{modak} is a Python library with a Rust backend used to generate data pipelines for scientific computing workflows. It uses a Rust-based task scheduler to create Python subprocesses which perform individual tasks such as data processing and plotting.\\
\textbf{Link:} \href{https://github.com/denehoffman/modak}{https://github.com/denehoffman/modak}\\



% Publications
\sectionheader{Publications}
ElKabbash, M., \textbf{Hoffman, N.}, Lininger, A. R., Jalil, S. A., Letsou, T., Hinczewski, M., Strangi, G., \& Guo, C. (2023). \textit{Fano Resonant Optical Coatings Platform for Full Gamut and High Purity Structural Colors.} Nature Communications, \textbf{14}(1). \href{https://doi.org/10.1038/s41467-023-39602-2}{DOI: 10.1038/s41467-023-39602-2}\\

ElKabbash, M., Letsou, T., Jalil, S. A., \textbf{Hoffman, N.}, Zhang, J., Rutledge, J., Lininger, A. R., Fann, C.-H., Hinczewski, M., Strangi, G., \& Guo, C. (2021). \textit{Fano-Resonant Ultrathin Film Optical Coatings.} Nature Nanotechnology, \textbf{16}(4), 440–446. \href{https://doi.org/10.1038/s41565-020-00841-9}{DOI: 10.1038/s41565-020-00841-9}\\

\textbf{Hoffman, N.}, \& Widom, M. (2021). \textit{Cluster Variation Method Analysis of Correlations and Entropy in BCC Solid Solutions.} Metallurgical and Materials Transactions A, \textbf{52}(5), 1551–1558. \href{https://doi.org/10.1007/s11661-021-06182-z}{DOI: 10.1007/s11661-021-06182-z}\\

ElKabbash, M., Sreekanth, K. V., Fraiwan, A., Cole, J., Alapan, Y., Letsou, T., \textbf{Hoffman, N.}, Guo, C., Sankaran, R. M., Gurkan, U. A., Hinczewski, M., \& Strangi, G. (2020). \textit{Ultrathin-Film Optical Coating for Angle-Independent Remote Hydrogen Sensing.} Measurement Science and Technology, \textbf{31}(11), 115201. \href{https://doi.org/10.1088/1361-6501/ab9fd8}{DOI: 10.1088/1361-6501/ab9fd8}\\

ElKabbash, M., Ilker, E., Letsou, T., \textbf{Hoffman, N.}, Yaney, A., Hinczewski, M., \& Strangi, G. (2017). \textit{Iridescence-Free and Narrowband Perfect Light Absorption in Critically Coupled Metal High-Index Dielectric Cavities.} Optics Letters, \textbf{42}(18), 3598. \href{https://doi.org/10.1364/ol.42.003598}{DOI: 10.1364/ol.42.003598}\\

ElKabbash, M., Sousa‐Castillo, A., Nguyen, Q., Mariño‐Fernández, R., \textbf{Hoffman, N.}, Correa‐Duarte, M. A., \& Strangi, G. (2017). \textit{Tunable Black Gold: Controlling the Near‐Field Coupling of Immobilized Au Nanoparticles Embedded in Mesoporous Silica Capsules.} Advanced Optical Materials, \textbf{5}(21). \href{https://doi.org/10.1002/adom.201700617}{DOI: 10.1002/adom.201700617}\\

\sectionheader{Collaboration Publications}
GlueX Collaboration, (2025). \textit{First Measurement of $a_2^0(1320)$ Polarized Photoproduction Cross Section}. Physical Review C, \textbf{112}(1). \href{https://doi.org/10.1103/jfzb-rfl4}{DOI: 10.1103/jfzb-rfl4}\\

GlueX Collaboration, (2025). \textit{First Measurement of the Total Compton Scattering Cross Section Between $6$ and $11$ GeV} (Version 1). arXiv. \href{https://doi.org/10.48550/ARXIV.2505.07994}{DOI: 10.48550/ARXIV.2505.07994}\\

GlueX Collaboration, (2025). \textit{Measurement of Spin-Density Matrix Elements in $\Delta^{++}(1232)$ Photoproduction}. Physics Letters B, \textbf{863}. \href{https://doi.org/10.1016/j.physletb.2025.139368}{DOI: 10.1016/j.physletb.2025.139368}\\

GlueX Collaboration, (2024). \textit{Upper Limit on the Photoproduction Cross Section of the Spin-Exotic $\pi_1(1600)$}. Physical Review Letters, \textbf{133}(26). \href{https://doi.org/10.1103/physrevlett.133.261903}{DOI: 10.1103/physrevlett.133.261903}\\

Pybus, J. R., et al. (GlueX Collaboration), (2024). \textit{Search for Axion-Like Particles Through Nuclear Primakoff Production Using the GlueX Detector}. Physics Letters B, \textbf{855}. \href{https://doi.org/10.1016/j.physletb.2024.138790}{DOI:\allowbreak\ 10.1016/\allowbreak j.physletb.2024.138790}\\

GlueX Collaboration, (2023). \textit{Measurement of Spin-Density Matrix Elements in $\rho(770)$ Production With a Linearly Polarized Photon Beam at $E_{\gamma} = 8.2$\textemdash $8.8$ GeV}. Physical Review C, \textbf{108}(5). \href{https://doi.org/10.1103/physrevc.108.055204}{DOI: 10.1103/physrevc.108.055204}\\
\newpage
GlueX Collaboration, (2023). \textit{Measurement of the $J/\psi$ Photoproduction Cross Section Over the Full Near-Threshold Kinematic Region}. Physical Review C, \textbf{108}(2). \href{https://doi.org/10.1103/physrevc.108.025201}{DOI: 10.1103/physrevc.108.025201}\\

GlueX Collaboration, (2022). \textit{Search for Photoproduction of Axionlike Particles at GlueX}. Physical Review D, \textbf{105}(5). \href{https://doi.org/10.1103/physrevd.105.052007}{DOI: 10.1103/physrevd.105.052007}\\

GlueX Collaboration, (2022). \textit{Measurement of Spin Density Matrix Elements in
$\Lambda(1520)$ Photoproduction at $8.2$\textemdash $8.8$ GeV}. Physical Review C, \textbf{105}(3). \href{https://doi.org/10.1103/physrevc.105.035201}{DOI: 10.1103/physrevc.105.035201}\\


\sectionheader{Work Experience}
\datedentry{\textbf{Engineer at \href{https://foliophotonics.com/}{Folio Photonics}}}{2019}
\narrowpar{}{Activities included data reading/writing experiments on multilayer films and developing software for testing and automation. I was tasked with developing programs to scan through layered disks and measure layer positions and thicknesses, as well as programs which ran testing procedures on physical devices using LabVIEW.}\\\\

% Languages
\sectionheader{Languages}
English (native), French (intermediate), Spanish (beginner)\\

% Skills
\sectionheader{Skills}
Rust, Python, C/C++, \LaTeX, Mathematica, ROOT, MPI\\
% References

\sectionheader{References}
\noindent \begin{tabular}{@{} l l}
 \href{http://www-meg.phys.cmu.edu/~schumach/}{Dr. Reinhard Schumacher} & \href{http://www.curtismeyer.com/index.php/main}{Dr. Curtis Meyer} \\
 Department of Physics &  Department of Physics  \\
 Carnegie Mellon University &  Carnegie Mellon University \\
 \small{\href{mailto:schumacher@cmu.edu}{schumacher@cmu.edu},\,+1\,(412)\,268-5177} & \small{\href{mailto:cmeyer@cmu.edu}{cmeyer@cmu.edu},\,+1\,(987)\,654-3210} \\
& \\
 \href{https://scholar.google.com/citations?user=cK_dVFAAAAAJ&hl=en}{Dr. Matthew Shepherd} & \href{http://nanoplasm.wrphysics.org/}{Dr. Giuseppe Strangi} \\
 Department of Physics & Department of Physics \\
 Indiana University & Case Western Reserve University \\
 \small{\href{mailto:mashephe@indiana.edu}{mashephe@indian.edu},\,+1\,(812)\,856-5808} & \small{\href{mailto:giuseppe.strangi@case.edu}{giuseppe.strangi@case.edu},\,+1\,(216)\,368-6918}
& \\
\href{https://scholar.google.com/citations?user=bhQY_u8AAAAJ&hl=en}{Dr. Mohamed ElKabbash} \\
Quantum Photonics Group \\
Massachusetts Institute of Technology \\
\small{\href{mailto:melkabba@mit.edu}{melkabba@mit.edu}} \\
\end{tabular}

\end{document}
